---
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# `kdata`: Korean Culture, Business, and Education Data

I will share Korea-related datasets and tools to analyze the data in `{kdata}` package. 

Let me know if you want me to share specific data that you are interested in.


## Datasets

```{r, echo=FALSE}

table <- tibble::tribble(
  ~Dataset, ~Contents, ~Status, ~Uploaded,
  "International Students Data", "A dataset containing information about international students in Korea, including their country of origin, visa type, and the number of students.", "Available", "2024-03-26",
  "International Students Data (Individual)", "A dataset containing information about all current individual international students in Korea, including their country of origin, sex, visa type, and schools", "Available (to-be-documented)", "2024-03-26",
  "International Students Data (Schools)", "A dataset containing information about  international students at each school/ university in Korea, containing information
  including their country of origin, visa type, major, TOPIK results and more", 
  "Available (to-be-documented)", "2024-03-26",
  "Korean Festivals Data", "A dataset containing detailed information about festivals in Korea, including names, locations, dates, and additional details in both Korean and English.", "Available", "2024-03-23"
)


table |> 
  kableExtra::kbl(
      format = "pipe",
      booktabs = TRUE,
      longtable = TRUE,
      #col.names = c(""),
      row.names = FALSE,
      align = "cc") |>
    kableExtra::kable_styling(full_width = F, "striped") 
```


## Installation

You can install the `kdata` package from [GitHub](https://github.com/) with:

``` r
devtools::install_github("kjayhan/kdata")
```

## How to cite this package?

When using the `kdata` package please cite the following:

-   Ayhan, Kadir Jun (2024). kdata: Korean Culture, Business, and Education Data. R package version 0.0.1.
